\documentclass[a4paper,11pt]{article}

\usepackage{url}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{float}
\usepackage{longtable}
%\usepackage{fullpage}
\usepackage{pstricks}
\usepackage{tikz}
\usepackage[absolute]{textpos}
\usepackage{import}
\usepackage{subfigure}
\usepackage{setspace}

\title{G53NMD Individual Assignment}
\author{Robert J. Golding (rjg08u)} \date{\today}

% Dutch style paragraph formatting
\setlength{\parskip}{1.3ex plus 0.2ex minus 0.2ex}
\setlength{\parindent}{0pt}

%\doublespacing
\onehalfspacing

\begin{document}
    \maketitle

    \begin{quote}
        \emph{Social media on a mobile platform is the pinnacle of excellence
        of new media. Discuss with examples the validity of this statement and
        how these technologies have changed the nature of design.}
    \end{quote}

    \section{Introduction}

    To understand what Social Media is (and also what it is \emph{not}), one
    must first get a feel for the related topics: Web 2.0 and User Generated
    Content. \cite{kaplan2010}

    Web 2.0 is a term that was first used in 2004 to describe a new way in
    which developers and end-users were starting to use the internet. It refers
    to the move away from the traditional model whereby content was created and
    published by individuals, remaining relatively static from that point on.
    Instead, the web became a collaborative platform upon which content could
    be continuously modified by users themselves.

    Though Web 2.0 does not refer to any particular technical ``update'' of the
    web itself, there are certain underlying technologies that are required for
    it to function. Among these are Adobe Flash---allowing videos, audio, and
    other forms of multimedia to be added to web pages---and RSS (Really Simple
    Syndication)---a method for retrieving content that is updated frequently,
    such as blog entries or news headlines.

    User Generated Content refers to, quite simply, content that has been
    generated by the \emph{users} of the web. According to the Organisation for
    Economic Co-operation and Development \cite{vickery2007}, user generated
    content must fulfill three requirements to be considered as such. It must:

    \begin{itemize}
        \item be published on a publicly accessibly website (or social
            networking website accessible to selected users);
        \item show a certain amount of creative effort (i.e. not be a direct
            re-publication of another work);
        \item have been created outside of professional routines and practices.
    \end{itemize}

    Though User Generated Content has been around prior to the rise of Web 2.0,
    the combination of technological, economic and social drivers make it more
    pervasive and difference from that which was observed in the first
    instance.

    Given these definitions, Social Media can be described as a group of
    internet based application that build upon the foundations of Web 2.0,
    allowing the creation and exchange of User Generated Content
    \cite{kaplan2010}.

    New media, meanwhile, has a different, wider meaning. Also, new media is
    a difficult term to define due to the extremely blurred line between
    ``new'' and ``old''. New media captures the development of new technologies
    (most notably the internet), and the remaking of more traditional forms of
    media \cite{flew2008}. The internet is the newest, most significant
    manifestation of new media, allowing information and \emph{knowledge} to be
    published and shared in ways and, indeed, at a speed never before
    possible.

    \bibliographystyle{alpha}
    \bibliography{references}

\end{document}
